\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-12-03 exps.tex
Updated exps.tex 2

The previous results show that HRTCS and Printer were the only examples
that the compiler was able to find \textit{d} without relaxing upper
bound of \texttt{delay}. 
This is because there are two influential factors in
determining the relaxation: 1) execution speed of a target platform and 
%Figure~\ref{fig:graph} shows the accuracy
%of our results by comparing differences between programmer specified
%upper bounds (Table~\ref{fig:benchlist}) and the actual bounds obtained
%using our techniques (Table~\ref{fig:comparison}).
2) the nature of the program that runs on this platform. Clock frequency
of the processor directly impacts the value of WCRT. On the other hand,
programmer can write a program such that large data (or control)
computations in a single logical tick increase WCRT of the program.
Assuming we do not change the architecture of the execution platform
(i.e. JOP), the size of relaxation can only be reduced by modifying the
benchmark programs such that the critical paths are broken up using
\texttt{pause} constructs, thereby reducing the WCRT.
Figure~\ref{fig:improv} shows segments of code from AECS whose WCRT is
reduced by such technique.

@@

In Figure~\ref{fig:improv-a}, the program simply checks for the id of a
person entering or exiting an intelligent room through the signals
called \texttt{EntryRequest} and \texttt{ExitRequest}, and verifies the
id using data logic written in Java (\texttt{isValidRequest}). We
identified this execution path caused lengthening the WCRT of the
program. In this case, we divide two consequtive statements, i.e.
\texttt{present} and \texttt{if}, by inserting \texttt{pause} such that
each of these statement is executed in two different ticks. The same
technique is applied to Motor example to reduce WCRT of the program.
Note that we can also optimize algorithms of the data computations used
in each Java method to reduce WCRT. However it is out of scope of this
paper, hence not discussed here.

The result of the upper bound relaxation with reduced WCRT is shown in
Figure~\ref{fig:graph}. As one can see from the Figure, the upper bounds
for delay statements in AECS/CD2 has been decreased by 11.81\% which is
higher than all those in Motor which ranges from 7.54 to 8.05\%. It is
because AECS has relatively a large amount of data computation while
Motor is a completely control-dominated program. Therefore, the result
shows that the size of the relaxation depends on how designers write
their program as well as types of the application (i.e. data or control
dominated).

@@

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot coordinates {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot coordinates {(Motor, 8.00)};
			\addplot coordinates {(Motor, 6.42)};
			\addplot coordinates {(Motor, 7.53)};
			\addplot coordinates {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph}
\end{figure}

>>>>

The previous results show that HRTCS and Printer were the only examples
that the compiler was able to find \textit{d} without relaxing upper
bound of \texttt{delay}. Figure~\ref{fig:graph1} shows the accuracy of
our results by comparing differences between programmer specified upper
bounds (Table~\ref{fig:benchlist}) and the actual bounds obtained using
our techniques (Table~\ref{fig:comparison}).

\begin{figure}[h!]
	\centering
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={HRTCS,Printer/CD1,Printer/CD2,AECS/CD2},
			height=5cm,
			width=9.5cm,
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
			ytick={0,0.5,...,2},
			enlarge x limits=0.3,
%      xlabel=Benchmark,
			x tick label style={rotate=45,font=\footnotesize},
			ylabel=Difference factor,
		]
			\addplot coordinates
			{(HRTCS,1)(Printer/CD1,1)(Printer/CD2,1)(AECS/CD2,1.94)};
			\addplot coordinates {(Printer/CD2, 1)(AECS/CD2, 1.94)};
	\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor},
			ytick={0,0.5,...,5},
			ymin={1.5},
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
%      extra y ticks={2.5},
%      extra y tick labels={asdf},
%      extra y tick style={grid=major},
			height=5cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(0.45,-0.44)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\addplot coordinates {(Motor, 2.60)};
			\addplot coordinates {(Motor, 2.63)};
			\addplot coordinates {(Motor, 4.39)};
			\addplot coordinates {(Motor, 2.92)};
			\addplot coordinates {(Motor, 2.69)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph1}
\end{figure}

There are two influential factors in determining the relaxation: 1)
execution speed of a target platform and 2) the nature of the program
that runs on this platform. Clock frequency of the processor directly
impacts the value of WCRT. On the other hand, programmer can write a
program such that large data (or control) computations in a single
logical tick increase WCRT of the program.  Assuming we do not change
the architecture of the execution platform (i.e. JOP), the differece
factor can can only be reduced by modifying the benchmark programs such
that the critical paths are broken up using \texttt{pause} constructs,
thereby reducing the WCRT.  Figure~\ref{fig:improv} shows segments of
code from AECS whose WCRT is reduced by such technique.

@@

In Figure~\ref{fig:improv-a}, the program simply checks for the id of a
person entering or exiting an intelligent room through the signals
called \texttt{EntryRequest} and \texttt{ExitRequest}, and verifies the
id using data logic written in Java (\texttt{isValidRequest}). We
identified this execution path caused lengthening the WCRT of the
program. In this case, we divide two consequtive statements, i.e.
\texttt{present} and \texttt{if}, by inserting \texttt{pause} such that
each of these statement is executed in two different ticks. The same
technique is applied to Motor example, which is purely
control-dominated, to reduce WCRT of the program. Note that we can also
optimize algorithms of the data computations used in each Java method to
reduce WCRT. However it is out of scope of this paper, hence not
discussed here.

The result of the upper bound relaxation with reduced WCRT is shown in
Figure~\ref{fig:graph2}. As one can see from the Figure, the upper
bounds for delay statements in AECS/CD2 have been decreased by 11.81\%
which is higher than all those in Motor which ranges from 7.54 to
8.05\%. It was as expected since amount of computation required
in control flow is mostly less demanding than data such that breaking
the critical paths in Motor did not reduce WCRT as much as AECS/CD2.
Therefore, we can see from the result that the size of the relaxation
depends on how designers write their program as well as typs of the
application (i.e. data or control dominated).

@@

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot coordinates {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot coordinates {(Motor, 8.00)};
			\addplot coordinates {(Motor, 6.42)};
			\addplot coordinates {(Motor, 7.53)};
			\addplot coordinates {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph2}
\end{figure}
